\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{\bibname}
\bibitem{PARTNER-JET}
JTAG ICE PARTNER-Jet，http://www.kmckk.co.jp/jet/，最終アクセス2009年1月14日

\bibitem{QNXMomentics}
QNX Momentics Tool Suite，http://www.qnx.co.jp/products/tools/，最終アクセス2009年1月14日

\bibitem{eBinder}
eBinder，http://www.esol.co.jp/embedded/ebinder.html，最終アクセス2009年1月14日

\bibitem{LKST}
LKST（Linux Kernel State Tracer) - A tool that records
traces of kernel state transition as events，http://oss.hitachi.co.jp/sdl/english/lkst.html，最終アクセス2009年1月14日

\bibitem{SystemTap}
Prasad, V., Cohen, W., Eigler, F. C., Hunt, M., Keniston, J. and Chen, B.: Locating system problems using dynamic instrumentation. Proc. of the Linux Symposium, Vol.2, pp.49–64, 2005.

\bibitem{LTTng}
Mathieu Desnoyers and Michel Dagenais.: The lttng tracer : A low impact performance and behavior monitor for gnu/linux. In OLS (Ottawa Linux Symposium) 2006, pp.209–224, 2006.

\bibitem{Dtrace}
R. McDougall, J. Mauro, and B. Gregg.: Solaris(TM) Performance and Tools: DTrace and MDB Techniques for Solaris 10 and OpenSolaris. Pearson Professional, 2006.

\bibitem{LTTV}
Mathieu Desnoyers and Michel R. Dagenais.:Tracing for Hardware, Driver, and Binary Reverse Engineering in Linux. Recon 2006

\bibitem{Chime}
OpenSolaris Project: Chime Visualization Tool for DTrace，http://opensolaris.org/os/project/dtrace-chime/，最終アクセス2009年1月14日

\bibitem{RFC3164}
RFC3164 The BSD syslog Protocol, http://www.ietf.org/rfc/rfc3164.txt，最終アクセス2009年1月14日

\end{thebibliography}
